Approximation as Differentiation: Notes

### 2025-05-16 main/formal-structures.tex
Tweaks to 2.2 intro.

For a total language where types denote sets, our goal is to interpret programs as Galois connections relating
approximations of their inputs to approximations of their outputs. Since these lattices of approximations
depends on the value being approximated, the semantics of every type $\tau$ must have both a ``conventional''
component, assigning $\tau$ to a set $X$, and an associated lattice of approximations $\partial X(x)$ for
every point $x \in X$. The semantics of expression $e$ of type $Y$ with a single free variable of type $X$
must then also have two components: a function $f: X \to Y$ giving the baseline (unapproximated) meaning of
the expression, plus a family of Galois connections $\partial f(x): \partial X(x) \to \partial Y(f(x))$ for
every $x \in X$ which can be used for slicing over that expression.

>>>>

We will consider a pure, total language, where types can be interpreted as sets. Our goal is to interpret
programs as Galois connections relating approximations of their inputs to approximations of their outputs.
Since these lattices of approximations depends on the value being approximated, the semantics of every type
$\tau$ must have both a ``conventional'' component, providing the set $X$ associated with $\tau$, plus an
associated lattice of approximations $\partial X(x)$ for every point $x \in X$. The semantics of an expression
$e$ of type $Y$ with a single free variable of type $X$ must then also have two components: a function $f: X
\to Y$ giving the baseline (unapproximated) meaning of the expression, plus a family of Galois connections
$\partial f(x): \partial X(x) \to \partial Y(f(x))$ for every $x \in X$ which can be used for slicing over
that expression.
